A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/DataStructures.tex
center diagram
add chapters

\chapter{Data Structures}
\label{chap:struct}
In this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework. We also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{figure/geometryNodes}
\caption{2D representations  of the \emph{geometry nodes} used in our \emph{reducer tree}.}
\label{fig:geometryNodes}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
\caption{Two examples of our \emph{reducer tree}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
By assigning materials to lower parts of the columns, the microfacet surface is created.
Right: a textured object with subsurface scattering properties is produced by first dividing the input shape using a \emph{stratum node}. Then, the outer layer is sliced into columns, which create a texture once materials are assigned. The inner part of the object obtains a material with given subsurface scattering properties.  
}
\label{fig:red1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{figure/tuner2.pdf}
\caption{A diagram of the \emph{tuner} workflow. Arrows indicate flow and type of information passed between the individual \emph{tuner} components.}
\label{fig:tuner0}
\end{figure}

>>>>

\chapter{Data Structures}
\label{chap:struct}
\biglet{I}{n} this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework. We also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/geometryNodes}
\caption{2D representations  of the \emph{geometry nodes} used in our \emph{reducer tree}.}
\label{fig:geometryNodes}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
\caption{Two examples of our \emph{reducer tree}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
By assigning materials to lower parts of the columns, the microfacet surface is created.
Right: a textured object with subsurface scattering properties is produced by first dividing the input shape using a \emph{stratum node}. Then, the outer layer is sliced into columns, which create a texture once materials are assigned. The inner part of the object obtains a material with given subsurface scattering properties.  
}
\label{fig:red1}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/tuner2.pdf}
\caption{A diagram of the \emph{tuner} workflow. Arrows indicate flow and type of information passed between the individual \emph{tuner} components.}
\label{fig:tuner0}
\end{figure}
